Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-29 proposal/prop.tex
prop.tex Fix some typos...

\begin{figure}
\begin{center}
\includegraphics[scale=0.38]{measure4.pdf}
\end{center}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates
  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
  and $\ket{\ps}$ respectively.  All possible vectors of the subspaces
  $\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
  circles, respectively. Within the circles, a dotted
  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
  green solid vectors are normalized
  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
\end{figure}

@@

The marriage of quantum mechanics and computer science first
envisioned and popularized by Feynman has created an awkward, but
opportune, moment. The embarrassing dilemma was concisely described by
Aaronson as follows. Consider the following three statements:
\begin{enumerate}
\item[(A)] Textbook quantum mechanics is correct
\item[(B)] There does not exist an efficient classical factoring
  algorithm
\item[(C)] The extended Church-Turing thesis that probabilistic Turing
  machines can efficiently simulate any physically realizable model of
  computation is correct.
\end{enumerate}
There is overwhelming evidence to support each of these
statements. The theoretical framework of quantum mechanics (A) has
withstood decades of experimental confirmation. Entire industries are
founded on the assumption (B) that algorithms like RSA are secure and
they also have withstood years of attempted attacks. Finally the
entire field of complexity theory in computer science which has also
withstood years of field testing rests, in essence, on assumption
(C). And yet one of these three statements \emph{must be false}! Indeed
if textbook quantum mechanics is false we concede (A). If it is
correct Shor's efficient factoring algorithm is realizable. If there
is a corresponding efficient classical factoring algorithm then we
concede (B). If not then we concede~(C).

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.38]{measure4.pdf}
\end{center}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates
  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
  and $\ket{\ps}$ respectively.  All possible real vectors of the subspaces
  $\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
  circles, respectively. Within the circles, a dotted
  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
  green solid vectors are normalized
  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
  $\times$ is the usual cross product in $\mathbb{R}^{3}$}
\end{figure}

@@

The marriage of quantum mechanics and computer science first
envisioned and popularized by Feynman has created an awkward, but
opportune, moment. The embarrassing dilemma was concisely described by
Aaronson as follows. Consider the following three statements:
\begin{enumerate}
\item[(A)] Textbook quantum mechanics is correct.
\item[(B)] There does not exist an efficient classical factoring
  algorithm.
\item[(C)] The extended Church-Turing thesis that probabilistic Turing
  machines can efficiently simulate any physically realizable model of
  computation is correct.
\end{enumerate}
There is overwhelming evidence to support each of these
statements. The theoretical framework of quantum mechanics (A) has
withstood decades of experimental confirmation. Entire industries are
founded on the assumption (B) that algorithms like RSA are secure and
they also have withstood years of attempted attacks. Finally the
entire field of complexity theory in computer science which has also
withstood years of field testing rests, in essence, on assumption
(C). And yet one of these three statements \emph{must be false}! Indeed
if textbook quantum mechanics is false we concede (A). If it is
correct Shor's efficient factoring algorithm is realizable. If there
is a corresponding efficient classical factoring algorithm then we
concede (B). If not then we concede~(C).
